---
title: "R Notebook"
output: html_notebook
---

Trying to improve the analysis by Bezy et al. Proceedings B manuscript.

```{r}
library(tidyverse)
library(readr)


```


Edited "Treatment Date" to "Treatment_Date"
```{r}

col.def <- cols(Rank = col_integer(),
                DateTime = col_datetime("%m/%d/%y %H:%M"),
                Treatment = col_factor(levels = c("SW", "ZN")),
                Treatment_Date = col_date("%m/%d/%y"),
                Interval = col_integer(),
                km = col_double(),
                CCL = col_double(),
                CCW = col_double(),
                Nesting = col_factor(c("Confirmed", "Unconfirmed")))

# I created two new variables: DOT and DOT1
# DOT is the day of treatment as in the day of year
# DOT1 is the number of days since treatment
exp.1 <- read_csv("data/Bezy_Olfaction_Experiment1.csv",
                  col_types = col.def) %>%
  mutate(DOT = lubridate::yday(Treatment_Date),
         DOT1 = DOT - min(DOT, na.rm = T))

lm.1 <- lm(Interval ~ Treatment + CCL, data = exp.1)
summary(lm.1)
```

The intercept is for the control. So, the treatment effect is >30 (hrs?) than the control. There was no CCL effect on Interval. I included only CCL because CCW and CCL are correlated. 



No effect in the distance moved. 


Experiment #2.

I modified variable names and factor levels. Also created a new variable (reencounter interval in minutes). See below.

```{r}
hms2min <- function(x){
  tmp <- strsplit(x, split = ":")
  if (is.na(tmp)) {
    out <- NA
  } else {
    tmp <- unlist(tmp)
    out <- as.numeric(tmp[1]) *60 + as.numeric(tmp[2]) + as.numeric(tmp[3])/60
  }
  return(out)
}

col.def.2 <- cols(Turtle = col_integer(),
                  Date = col_date("%m/%d/%y"),
                  Treatment_Time = col_time("%h:%M %p"),
                  Treatment = col_factor(c("SW", "ZN")),
                  Application = col_factor(c("E", "I_E")),
                  Time_Reencounter = col_character(),
                  Reencounter_Interval = col_character(),
                  Nesting = col_factor(c("Confirmed", "Unconfirmed")))

exp.2 <- read_csv("data/Bezy_Olfaction_Experiment2.csv",
                  col_types = col.def.2) %>%
  mutate(Reencounter_min = lapply(Reencounter_Interval, 
                                  FUN = hms2min) %>% 
           unlist())

lm.2 <- lm(Reencounter_min ~ Treatment, 
           data = exp.2 %>% filter(Application == "E"))
summary(lm.2)
```


```{r}
lm.2.1 <- lm(Reencounter_min ~ Treatment, data = exp.2)
summary(lm.2.1)
```

